ISF Grant

### 2017-09-26 article.tex
correctness property

>>>>

\subsection{Correctness and Progress properties}
Correctness property specifies the requirments for an implementation to be considerd correct. Linearizability, presented by Wang and Herliry [*], is the most common correctness property in use for shared memory objects. Roughtly speaking, linearizability requires that operations on objects appear to take effect instantaneously in some serial order, while preserving the happens before relation, i.e., if op1 ends before op2 begins, then op1 should precede op2 in the serial order. Linearizability has no notion of an aborted or failed operation, and requires that a process finish one operation before it invokes the next. The criteria according to which implementations that support recovered processes are correct remain unclear.
